<<<<<<< HEAD
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

BondHealth is a comprehensive digital healthcare ecosystem designed to unify patient care
across multiple healthcare providers. This project addresses the critical challenge of frag-
mented medical records by creating a centralized platform where patients' medical history,
appointments, and lab results are securely accessible across all connected hospitals. The
system features role-based dashboards for patients, doctors, hospital administrators, and lab
technicians. Key functionalities include appointment scheduling (booking, rescheduling, and
cancellation), electronic medical records management, lab report integration, prescription
management, doctor leave tracking, and a public review system. Built with Node.js and Express
on the backend, PostgreSQL for data persistence, and vanilla JavaScript with Tailwind CSS
for the frontend, BondHealth demonstrates a production-ready healthcare management
solution. The platform implements robust authentication using JWT tokens, role-based
access control, and comprehensive API endpoints for all operations. With features like
appointment management, leave tracking for doctors, and a dynamic review system,
BondHealth provides a seamless experience for all stakeholders in the healthcare delivery
chain.

\vspace{0.5cm}
\noindent\textbf{Keywords:} Healthcare Management System, Electronic Medical Records, Patient
Portal, Hospital Management, Node.js, PostgreSQL, JWT Authentication, Role-Based
Access Control
=======
\thispagestyle{footeronly}
\addcontentsline{toc}{chapter}{ABSTRACT}
\begin{center}
{\Large \textbf{ABSTRACT}}
\end{center}
\noindent
BondHealth is a comprehensive digital healthcare ecosystem designed to unify patient care across multiple healthcare providers. This project addresses the critical challenge of fragmented medical records by creating a centralized platform where patients' medical history, appointments, and lab results are securely accessible across all connected hospitals.
\noindent
The system features role-based dashboards for patients, doctors, hospital administrators, and lab technicians. Key functionalities include appointment scheduling, electronic medical records management, lab report integration, prescription management, and a public review system. Built with Node.js and Express on the backend, PostgreSQL for data persistence, and vanilla JavaScript with Tailwind CSS for the frontend, BondHealth demonstrates a production-ready healthcare management solution.
\noindent
The platform implements robust authentication using JWT tokens, role-based access control, and comprehensive API endpoints for all operations. With features like real-time appointment management, leave tracking for doctors, and a dynamic review system, BondHealth provides a seamless experience for all stakeholders in the healthcare delivery chain.
\noindent
\textbf{Keywords:} Healthcare Management System, Electronic Medical Records, Patient Portal, Telemedicine, Hospital Management, Node.js, PostgreSQL, JWT Authentication, Role-Based Access Control
>>>>>>> 28295e1c39248834c6ac8037f8ae5d0a6abb5e3f
