\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{References}

% Node.js Documentation
\bibitem{nodejs}
Node.js Foundation. (2024). \textit{Node.js v18.x Documentation}. Retrieved from https://nodejs.org/en/docs/

% Express.js Documentation
\bibitem{express}
Express.js Team. (2024). \textit{Express - Node.js web application framework}. Retrieved from https://expressjs.com/

% PostgreSQL Documentation
\bibitem{postgresql}
PostgreSQL Global Development Group. (2024). \textit{PostgreSQL 15 Documentation}. Retrieved from https://www.postgresql.org/docs/15/

% Neon Database Documentation
\bibitem{neon}
Neon. (2024). \textit{Neon Serverless Postgres Documentation}. Retrieved from https://neon.tech/docs

% JWT (JSON Web Tokens)
\bibitem{jwt}
Jones, M., Bradley, J., \& Sakimura, N. (2015). \textit{JSON Web Token (JWT)}. RFC 7519. Internet Engineering Task Force. Retrieved from https://tools.ietf.org/html/rfc7519

% bcrypt
\bibitem{bcrypt}
Provos, N., \& Mazi{\`e}res, D. (1999). \textit{A Future-Adaptable Password Scheme}. Proceedings of the 1999 USENIX Annual Technical Conference. Retrieved from https://www.usenix.org/legacy/events/usenix99/provos/provos.pdf

% Tailwind CSS
\bibitem{tailwind}
Tailwind Labs. (2024). \textit{Tailwind CSS Documentation}. Retrieved from https://tailwindcss.com/docs

% Bootstrap
\bibitem{bootstrap}
Bootstrap Team. (2024). \textit{Bootstrap 5 Documentation}. Retrieved from https://getbootstrap.com/docs/5.3/

% Font Awesome
\bibitem{fontawesome}
Fonticons, Inc. (2024). \textit{Font Awesome Documentation}. Retrieved from https://fontawesome.com/docs

% World Health Organization - Digital Health
\bibitem{who}
World Health Organization. (2021). \textit{Global strategy on digital health 2020-2025}. Geneva: World Health Organization. Retrieved from https://www.who.int/docs/default-source/documents/gs4dhdaa2a9f352b0445bafbc79ca799dce4d.pdf

% HIPAA Compliance
\bibitem{hipaa}
U.S. Department of Health \& Human Services. (2023). \textit{Summary of the HIPAA Privacy Rule}. Retrieved from https://www.hhs.gov/hipaa/for-professionals/privacy/laws-regulations/index.html

% GDPR
\bibitem{gdpr}
European Parliament and Council. (2016). \textit{General Data Protection Regulation (GDPR)}. Official Journal of the European Union. Retrieved from https://eur-lex.europa.eu/legal-content/EN/TXT/?uri=CELEX\%3A32016R0679

% ABDM - India's Health Mission
\bibitem{abdm}
National Health Authority. (2024). \textit{Ayushman Bharat Digital Mission (ABDM)}. Government of India. Retrieved from https://abdm.gov.in/

% REST Architecture
\bibitem{rest}
Fielding, R. T. (2000). \textit{Architectural Styles and the Design of Network-based Software Architectures}. Doctoral dissertation, University of California, Irvine. Retrieved from https://www.ics.uci.edu/~fielding/pubs/dissertation/top.htm

% Agile Methodology
\bibitem{agile}
Beck, K., et al. (2001). \textit{Manifesto for Agile Software Development}. Retrieved from https://agilemanifesto.org/

% Git Version Control
\bibitem{git}
Chacon, S., \& Straub, B. (2014). \textit{Pro Git} (2nd ed.). Apress. Retrieved from https://git-scm.com/book/en/v2

% LaTeX Documentation
\bibitem{latex}
Lamport, L. (1994). \textit{LaTeX: A Document Preparation System} (2nd ed.). Addison-Wesley Professional.

% Software Testing
\bibitem{softwaretesting}
Myers, G. J., Sandler, C., \& Badgett, T. (2011). \textit{The Art of Software Testing} (3rd ed.). John Wiley \& Sons.

% Database Design
\bibitem{database}
Elmasri, R., \& Navathe, S. B. (2016). \textit{Fundamentals of Database Systems} (7th ed.). Pearson.

% Web Development - JavaScript
\bibitem{javascript}
Flanagan, D. (2020). \textit{JavaScript: The Definitive Guide} (7th ed.). O'Reilly Media.

% Web Security
\bibitem{security}
Stallings, W. (2016). \textit{Cryptography and Network Security: Principles and Practice} (7th ed.). Pearson.

% Healthcare Management Systems - Research Paper
\bibitem{healthcareit}
Adler-Milstein, J., \& Jha, A. K. (2017). \textit{HITECH Act Drove Large Gains In Hospital Electronic Health Record Adoption}. Health Affairs, 36(8), 1416-1422. doi: 10.1377/hlthaff.2016.1651

% Telemedicine
\bibitem{telemedicine}
World Health Organization. (2022). \textit{Telemedicine: Opportunities and developments in Member States}. Retrieved from https://www.who.int/publications/i/item/9789240044564

% Hospital Management Systems
\bibitem{hms}
Kumar, S., \& Sharma, R. (2020). \textit{Design and Implementation of Hospital Management System}. International Journal of Computer Applications, 175(5), 35-40. doi: 10.5120/ijca2020920556

% JWT Best Practices
\bibitem{jwtbest}
Auth0. (2024). \textit{JWT Handbook}. Retrieved from https://auth0.com/resources/ebooks/jwt-handbook

% bcrypt Best Practices
\bibitem{bcryptbest}
OWASP Foundation. (2024). \textit{Password Storage Cheat Sheet}. Retrieved from https://cheatsheetseries.owasp.org/cheatsheets/Password_Storage_Cheat_Sheet.html

% Neon Database - Serverless Postgres
\bibitem{neonarch}
Neon. (2024). \textit{Building Serverless PostgreSQL: Architecture Deep Dive}. Neon Tech Blog. Retrieved from https://neon.tech/blog/architecture-deep-dive

% Express.js Best Practices
\bibitem{expressbest}
Express.js Team. (2024). \textit{Express.js Production Best Practices}. Retrieved from https://expressjs.com/en/advanced/best-practice-performance.html

% RESTful API Design
\bibitem{restful}
Microsoft. (2024). \textit{RESTful web API design}. Microsoft Docs. Retrieved from https://docs.microsoft.com/en-us/azure/architecture/best-practices/api-design

% Healthcare Data Standards
\bibitem{hl7}
HL7 International. (2024). \textit{HL7 FHIR Release 4}. Retrieved from https://hl7.org/fhir/

% Digital Health in India
\bibitem{indiahealth}
Ministry of Health and Family Welfare. (2023). \textit{National Digital Health Blueprint}. Government of India. Retrieved from https://main.mohfw.gov.in/sites/default/files/Final\%20NDHB\%20report_0.pdf

% WebRTC for Telemedicine
\bibitem{webrtc}
WebRTC Project. (2024). \textit{WebRTC Documentation}. Retrieved from https://webrtc.org/getting-started/overview

% Containerization - Docker
\bibitem{docker}
Docker Inc. (2024). \textit{Docker Documentation}. Retrieved from https://docs.docker.com/

% Kubernetes
\bibitem{kubernetes}
The Kubernetes Authors. (2024). \textit{Kubernetes Documentation}. Retrieved from https://kubernetes.io/docs/home/

% GitHub Actions
\bibitem{githubactions}
GitHub. (2024). \textit{GitHub Actions Documentation}. Retrieved from https://docs.github.com/en/actions

% NPM
\bibitem{npm}
npm, Inc. (2024). \textit{npm Documentation}. Retrieved from https://docs.npmjs.com/

% Cookie Security
\bibitem{cookies}
Mozilla Developer Network. (2024). \textit{HTTP cookies}. Retrieved from https://developer.mozilla.org/en-US/docs/Web/HTTP/Cookies

% SQL Injection Prevention
\bibitem{sqlinjection}
OWASP Foundation. (2024). \textit{SQL Injection Prevention Cheat Sheet}. Retrieved from https://cheatsheetseries.owasp.org/cheatsheets/SQL_Injection_Prevention_Cheat_Sheet.html

% Cross-Site Scripting Prevention
\bibitem{xss}
OWASP Foundation. (2024). \textit{XSS Prevention Cheat Sheet}. Retrieved from https://cheatsheetseries.owasp.org/cheatsheets/Cross_Site_Scripting_Prevention_Cheat_Sheet.html

% Responsive Web Design
\bibitem{responsive}
Marcotte, E. (2010). \textit{Responsive Web Design}. A List Apart. Retrieved from https://alistapart.com/article/responsive-web-design/

% User Interface Design Principles
\bibitem{uidesign}
Nielsen, J. (2012). \textit{Usability 101: Introduction to Usability}. Nielsen Norman Group. Retrieved from https://www.nngroup.com/articles/usability-101-introduction-to-usability/

% Git Workflow
\bibitem{gitflow}
Atlassian. (2024). \textit{Gitflow Workflow}. Retrieved from https://www.atlassian.com/git/tutorials/comparing-workflows/gitflow-workflow

\end{thebibliography}